\thetitle

### 2020-11-17 writing/mutate.tex
adding  better explanation of interesting scenarios

The first criterion simply validates that the debugging scenario concerns
a type-level mistake. However, The second and third criteria require 
more explanation.  The second one stipulates that the mistake is
detectable under Erasure to ensure that it is detectable by all three
semantics.  This is a direct consequence of~\citet{gfd-oopsla-2019}'s
theorem that a run time error under Erasure implies a run time
error under both Transient and Natural.  It is worth noting that this
criterion excludes from consideration the very interesting scenarios where Natural or
Transient can detect a mistake but Erasure cannot, and thus it favors
Erasure.  However, our goal here is to test the rational programmer across
these three semantics, and thus we opt for a setting where all of them
notice the mistake.

The third criterion aims to capture debugging scenarios with a specific
kind of run time error: one produced because of the interaction between the buggy
portion of the program with the rest of the program.  In those cases, the rational programmer
may need to examine several pieces of the program to locate the source of the faulty interaction.
In technical terms, we mark these scenarios by
analyzing the stack trace of a run time error.  If the stack trace mentions at
least two distinct components, then this is accurate evidence of
interaction.  We require a third component because our benchmarks come
with a driver component which is present in the stack trace of all run
time errors.

@@

With this definition in hand, we analyze how effective our mutators
are for turning the benchmarks into interesting debugging scenarios.
Indeed the mutators produce at least 72192 interesting debugging scenarios
across all mutants --- there are potentially many more but this is how
many we examined. 
Figure~\ref{fig:mutant-breakdown} breaks down the interesting
debugging scenarios produced  for each benchmark by mutator 
but counts are cut off at 50. The mutators produce at least 40 interesting
scenarios for every benchmark, and these scenarios originate from at
least four different mutators per benchmark.  Thus the mutators result in 
a sizeable and diverse population of scenarios for every benchmark.
Furthermore, every mutator contributes scenarios to at least one
benchmark. Especially some mutators  target specific features of
benchmarks, which
justifies their inclusion. For
instance the class-focused mutators are effective in \texttt{take5}
which jives with the fact that \texttt{take5} is the benchmark with 
the most extensive use of object-oriented features.

>>>>

The first criterion simply validates that the debugging scenario concerns
an actual type-level mistake. However, The second and third criteria require 
more explanation.  The second one stipulates that the mistake is
detectable under Erasure to ensure that it is detectable by all three
semantics.   Whether a scenario produces a run time error largely depends on 
the underlying semantics but \citet{gfd-oopsla-2019}
show that a run time error under Erasure implies a run time
error under both Transient and Natural. Thus the criterion aligns
interesting debugging scenarios with our lowest denominator, Erasure, 
and excludes  from consideration the very interesting scenarios indeed where Natural or
Transient can detect a mistake but where Erasure is powerless. Of course this choice favors
Erasure over Transient and Natural and, for the same reason, Transient over
Natural. We consider some form of bias towards one or the other semantics
unavoidable no matter how we define interesting debugging scenarios and we
opt for tipping the scales in favor of the theoretically weakest
semantics.

The third criterion aims to capture debugging scenarios with a specific
kind of run time error: one produced because of the interaction between the buggy
portion of the program with the rest of the program.  In these cases, the rational programmer
may need to examine several pieces of the program to locate the source of the faulty interaction.
In technical terms, we reliably mark these scenarios by
analyzing the stack trace of a run time error.  If the stack trace mentions at
least two distinct components, then this indicates interaction.  We require a third component because our benchmarks come
with a driver component which is present in the stack trace of all run
time errors. In essence, this last criterion excludes a large number of
trivial to debug, and thus ineffective, scenarios that error immediately when their mutated component is
evaluated.

@@

With the definition of interesting debugging scenarios in hand, we analyze how effective our mutators
are for turning the benchmarks into interesting debugging scenarios.
Indeed the mutators produce at least 72192 interesting debugging scenarios
across all mutants --- there are potentially many more but this is how
many we examined. 
Figure~\ref{fig:mutant-breakdown} breaks down the interesting
debugging scenarios produced  for each benchmark by mutator 
but counts are cut off at 50. The mutators produce at least 40 interesting
scenarios for every benchmark, and these scenarios originate from at
least four different mutators per benchmark.  Thus the mutators result in 
a sizeable and diverse population of scenarios for every benchmark.
Furthermore, every mutator contributes scenarios to at least one
benchmark. Especially some mutators  target specific features of
benchmarks, which
justifies their inclusion. For
instance the class-focused mutators are effective in \texttt{take5}
which jives with the fact that \texttt{take5} is the benchmark with 
the most extensive use of object-oriented features.
